---
title: "Run All"
output: html_notebook
---

* Primary Author: name, email.
* Project Started: 12/18/2018
* Project Close Out: 
* Package Snapshot date: 12/18/2018.
* System: Windows 10/ Mac OSX.
* R Version: 

*This script will run (in order) all neccessary scripts and Rmds to generate final output.*

#Project 
##Overview

High level description

## Details

+ source data stored where?
+ Project partners
+ final hand off was what...


## Scripts
### Overview Table

| Input              	| Code               	| Output             	|
|--------------------	|--------------------	|--------------------	|
| raw data           	| smell-test.R       	| wisdom             	|
| raw data           	| wrangleR 	          | data_cleaned       	|
| xxxxxxxxxxxxxxxxxx 	| xxxxxxxxxxxxxxxxxx 	| xxxxxxxxxxxxxxxxxx 	|
| xxxxxxxxxxxxxxxxxx 	| xxxxxxxxxxxxxxxxxx 	| xxxxxxxxxxxxxxxxxx 	|
_use tab to fix lineup_


### Always Run Scripts

```{r}
source(here::here("always_run","libraries.R"))
source(here::here("always_run","functions.R"))
source(here::here("always_run","options.R"))

```


### Clean Up Scripts
description

```{r}
#source(here::here("cleanup","import.R"))
#rmarkdown::render(here::here('cleanup','import.Rmd'))
```

### Analysis Scripts
description

```{r}

```


### Modeling Scripts
description

```{r}

```


#Project Template Readme

## Project start up checklist

* checkpoint 
* git 
* ????

## Project close out checklist

* final checkpoint date entered
* confirm full run with raw data
* final location of raw data documented
* ???

